%\addcontentsline{toc}{section}{Examiner Approval Sheet}
\section*{Examiner Approval Sheet}
We, the undersigned members of the Board of Examiners of the final open defense by Kibrom
Esayas, have read and evaluated his thesis entitled \textbf{“Model predictive control of active
voltage source rectifier's output voltage under unbalanced grid voltage conditions”},
and examined the candidate. This is, therefore, to certify that the thesis has been accepted in
partial fulfillment of the requirements for the degree.
\begin{table}[H]
    \centering
    \def\arraystretch{1.5}
    \begin{tabular}{lp{2.3in}p{1.5in}c}
          & Approved by                  & Signature & Date          \\
          &                              &           &               \\
        1 & Gebremicheal Te-ame(Dr.-Ing) & \underline{\hspace{1.5in}}          & \underline{\hspace{1in}} \\
          & Advisor                      &           &               \\
        2 & \underline{\hspace{1.5in}}   & \underline{\hspace{1.5in}}          & \underline{\hspace{1in}} \\
          & Internal Examiner            &           &               \\
        3 & \underline{\hspace{1.5in}}   & \underline{\hspace{1.5in}}          & \underline{\hspace{1in}} \\
          & External Examiner            &           &               \\
        4 & \underline{\hspace{1.5in}}   & \underline{\hspace{1.5in}}          & \underline{\hspace{1in}} \\
          & Chairperson, Department      &           &               \\
    \end{tabular}
\end{table}
\thispagestyle{empty}
\newpage
\setcounter{page}{1}
\chapter*{Declaration}
\addcontentsline{toc}{chapter}{Declaration}
I hereby declare that this MSc thesis entitled \textbf{“Model predictive control of active voltage
source rectifier's output voltage under unbalanced grid voltage conditions”} is my
original work and has not been presented for a degree in any other university, and all sources of
material used for this thesis have been duly acknowledged.\par
\begin{table}[H]
    \centering
    \def\arraystretch{2}
    \begin{tabular}{p{2.3in}p{1.8in}c}
        Submitted by  & Signature & Date          \\
        Kibrom Esayas & \underline{\hspace{1.5in}}          & \underline{\hspace{1.5in}}
    \end{tabular}
\end{table}
This MSc thesis entitled \textbf{“Model predictive control of active voltage source rectifier's
output voltage under unbalanced grid voltage conditions”} has been submitted for examination 
with my approval as thesis advisor.
\begin{table}[H]
    \centering
    \def\arraystretch{2}
    \begin{tabular}{p{2.3in}p{1.8in}c}
        Advisor & Signature & Date\\
        Gebremicheal Te-ame(Dr.-Ing)  &\underline{\hspace{1.5in}} & \underline{\hspace{1.5in}} \\
    \end{tabular}
\end{table}

\newpage
\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}
First and foremost, I would like to thank God for granting me the strength, and perseverance to successfully
complete this research and my master's studies. \par
My deepest gratitude belongs to my beloved parents, Esayas and Tifito. Thank you for your unconditional love, endless patience,
and the profound sacrifices you have made for my education. Your unwavering support and belief in me over the years have been my
greatest source of inspiration and strength. I am also deeply grateful to my brothers, Daniel and Eyob, for always standing by
my side. Thank you for your constant encouragement, understanding, and the continuous support you have given me.\par
I would also like to express my deepest and most sincere gratitude to my advisor, Gebremicheal Te-ame (Dr.-Ing),
for his invaluable guidance, constructive feedback, and continuous support throughout this thesis. Special thanks go to my dear
friends, Mikeyas, Nahusenay, and Yebrah. Thank you for your exceptional support.\par
Finally, I want to thank everyone at Mekelle University, and all those who, directly or indirectly, contributed to the successful
completion of this thesis.\par

\newpage
\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
This thesis presents a Model Predictive Control (MPC) strategy for a three-phase Active Voltage Source Rectifier (VSR)
operating under unbalanced and distorted grid conditions. Conventional control methods often struggle to maintain 
power quality during grid faults, leading to significant DC-link voltage ripples and harmonic distortion in the input
currents. To address these challenges, this research develops a robust control framework that integrates a mathematical
model of the VSR based on symmetrical sequence decomposition.\par
The proposed system utilizes a cascaded control structure, employing an outer-loop MPC to regulate the DC-link energy
and an inner-loop PI controller for precise current tracking. A comprehensive discrete-time prediction model is
derived to forecast the future behavior of the positive and negative sequence components. A specialized cost function
is designed and minimized to generate optimal control references, specifically targeting the suppression of second-order
power oscillations (100 Hz ripple) and the mitigation of negative-sequence currents.\par
The performance of the proposed controller is validated through extensive simulations in the MATLAB/Simulink environment
using both linear and nonlinear switching models. Test scenarios include balanced grid conditions and various unbalanced
fault types. The results demonstrate that the proposed MPC strategy achieves superior DC-link voltage regulation and
reduced harmonic distortion compared to traditional control methods, effectively ensuring unity power factor and stable
operation even under grid unbalance.\par
\bigskip

\textbf{Keywords:  Active Rectifier, Voltage Source Rectifier (VSR), Model Predictive Control (MPC),
 Unbalanced Grid Conditions, Symmetrical Components}

