\chapter{Simulation Result \& Discussion}\label{SimulationResult}
\section{Introduction}
In chapter three, an Model Predictive controller (MPC) and a PI controller were designed to control
3-phase active rectifier system. In this chapter, the performance of both controllers will be evaluated
through simulation results. The simulation is carried out in MATLAB/Simulink environment\footnote{All Models in this thesis can be found in this github page https://github.com/KibromE/MScThesisDoc }, 
and the system parameters used in the simulation are based on the values shown in Table \ref{tab:system_parameters} 
for a 3-phase active rectifier system.\par
\begin{table}[htbp]
    \centering
    \caption{System Parameters of 3-Phase Active Rectifier}
    \begin{tabular}{|l|c|c|}
        \hline
        \textbf{Parameter} & \textbf{Symbol} & \textbf{ Value} \\ \hline
        AC Source Voltage (line-line RMS) & $V_{LL}$ & 400 V \\ \hline
        AC Source Frequency & $f$ & 50 Hz \\ \hline
        Input Inductance & $L_{in}$ & 2 mH \\ \hline
        Input Resistance & $R_{in}$ & 0.1 $\Omega$ \\ \hline
        DC Link Capacitance & $C_{dc}$ & 1500 $\mu$F \\ \hline
        DC Link Voltage & $V_{dc}$ & 700 V \\ \hline
        Load Resistance & $R_{load}$ & 100 $\Omega$ \\ \hline
        Switching Frequency & $f_{sw}$ & 10 kHz \\ \hline
    \end{tabular}
    \label{tab:system_parameters}
\end{table}
The controller parameters used in the simulation are based on the values shown in Table \ref{tab:controller_parameters} which
are selected based on the tuning process described in chapter three. The MPC parameters are chosen to balance the trade-off 
between control performance and computational complexity, while the inner current loop parameters are selected to ensure stability
and fast response of the current control loop.\par
\begin{table}[htbp]
    \centering
    \caption{Controller Parameters}
    \begin{tabular}{|l|c|c|}
        \hline
        \textbf{Parameter} & \textbf{Symbol} & \textbf{ Value} \\ \hline
        MPC Prediction Horizon & $N_p$ & 10 \\ \hline
        MPC Control Horizon & $N_c$ & 10 \\ \hline
        MPC Weighting for Control Input & $\lambda_R$ & 20e6 \\ \hline
        MPC Weighting for Energy tracking & $\lambda_{W}$ & 160 \\ \hline
        MPC Weighting for Reactive reduction & $\lambda_{Q}$ & 500 \\ \hline
        MPC Weighting for Ripple Suppression & $\lambda_{Rip}$ & 2e6 \\ \hline
        Maximum Control Input Constraint & $u_{max}$ & 50 A \\ \hline
        Inner Current Loop Proportional Gain & $K_{p,inner}$ & 0.1 \\ \hline
        Inner Current Loop Integral Gain & $K_{i,inner}$ & 50 \\ \hline
        Inner Current Loop Bandwidth & $f_{bw,inner}$ & 1000 Hz \\ \hline
        Inner Current Loop Sampling Time & $T_{s,inner}$ & 10 $\mu$s \\ \hline
        Outer Voltage Loop Sampling Time & $T_{s,outer}$ & 100 $\mu$s \\ \hline
    \end{tabular}
    \label{tab:controller_parameters}
\end{table}
The simulation is conducted for both a linear mathematical model of the system and a nonlinear switching model.
The linear model is used to evaluate the control performance under ideal conditions, while the nonlinear switching model is used
to assess the robustness of the controllers under more realistic conditions that include switching effects and non-idealities.\par
Both models are subjected to various grid conditions, including balanced and unbalanced scenarios, to evaluate the controllers' 
performance in regulating the DC link voltage and maintaining power quality. The simulation results will be analyzed and compared 
to determine the effectiveness of the MPC and PI controllers in different operating conditions.\par
The test scenarios for the simulation are listed in Table \ref{tab:test_scenarios}, which include both balanced and unbalanced 
grid conditions to evaluate the controllers' performance under different operating conditions.\par
\begin{table}[htbp]
    \centering
    \caption{Test Scenarios for Simulation}
\begin{tabular}{|l|p{7.5cm}|m{3.5cm}|}
        \hline
        \textbf{Test Scenario} & \textbf{Description} & \textbf{Voltage (V)}\\ \hline
        Balanced Grid  & All three phases have equal voltage magnitudes and are 120 degrees apart in phase. & 
        \begin{tabitemize}
            \item $v_a = 230 \angle 0^\circ$
            \item $v_b = 230 \angle 240^\circ$
            \item $v_c = 230 \angle 120^\circ$
        \end{tabitemize} \\ \hline
        Type G Unbalanced  & One phase drops slightly; two others drop significantly with a shift phase. &
        \begin{tabitemize}
            \item $v_a = 214.6 \angle 0^\circ$
            \item $v_b = 192.1 \angle 236^\circ$
            \item $v_c = 192.1 \angle 124^\circ$
        \end{tabitemize} \\ \hline
        Type F Unbalanced  & One phase drops significantly, and the other two phases drop slightly with a phase shift. & 
        \begin{tabitemize}
            \item $v_a = 184 \angle 0^\circ$
            \item $v_b = 207.4 \angle 243.7^\circ$
            \item $v_c = 207.4 \angle 116.3^\circ$
        \end{tabitemize} \\ \hline
        Type B Unbalanced  & One phase has a reduced voltage magnitude while the other two phases remain unaffected. & 
        \begin{tabitemize}
            \item $v_a = 185 \angle 0^\circ$
            \item $v_b = 230 \angle 240^\circ$
            \item $v_c = 230 \angle 120^\circ$
        \end{tabitemize} \\ \hline
    \end{tabular}
    \label{tab:test_scenarios}
\end{table}
\section{Simulation Results}
\subsection{Simulation of Linear Mathematical Model}


\subsection{Simulation of Nonlinear Switching Model}
